---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SSURGOPortal

<!-- badges: start -->
<!-- badges: end -->

The goal of SSURGOPortal is to provide a simple R interface to the 'SSURGO Portal' Python tools. Providing an R wrapper around the SSURGO Portal API allows users to automate many of the operations they might normally achieve through the graphical user interface.

## Installation

You can install the development version of {SSURGOPortal} like so:

``` r
remotes::install_github("brownag/SSURGOPortalR")
```

## Example

This is example shows how to install the .PYZ file to a standard location:

```{r libr, eval=TRUE}
library(SSURGOPortal)
```

```{r install, eval=FALSE}
install_ssurgo_portal()
```

The above installation routine places the SSURGO Portal file in a platform-specific folder: `ssurgo_portal_dir("data")`

To verify everything is set up and working, we can send the `"getstatus"` command, like so: 

```{r}
ssurgo_portal("getstatus")
```

See the documentation for `ssurgo_portal()` (`?ssurgo_portal`) for other available commands and more examples.

In general, a command is structured as JSON with a specific request name and various other parameters. This JSON string is passed via the terminal to the .pyz file and Python interpreter. 

We can inspect the commands that are generated using `command_only=TRUE`

For example, here is a sample `"copytemplate"` request to create a new GeoPackage database called `"test.gpkg"` from a template:

```{r}
ssurgo_portal("copytemplate", 
              templatename = "GeoPackage", 
              folder = "sample_gpkg", 
              filename = "test", 
              overwrite = TRUE, 
              command_only = TRUE)
```

Now after inspecting the command, we can actually run it:

```{r}
ssurgo_portal("copytemplate", 
              templatename = "GeoPackage", 
              folder = "sample_gpkg", 
              filename = "test", 
              overwrite = TRUE)
```

## Cross-platform Support

This package applies patches to attempt to make the .PYZ contents minimally compatible with Linux and macOS. This feature is experimental and intended to provide feedback for future development. The configuration routine that installs the bundled Windows .whl files will be triggered on non-Windows platforms (and should be expected to fail). 

To prepare your Python system or virtual environment on other platforms, run `python -m pip install bottle gdal` (or similar) to make sure that the required modules are already installed before invoking the SSURGO Portal tools.

If you encounter other problems on non-Windows platforms, file an issue in the [issue tracker](https://github.com/brownag/SSSURGOPortalR/issues).
